Practical Parametricity for GADTs

### 2020-07-23 20-gadts/inf-rules.tex
relations on wCPO again?

To accommodate GADTs, we will need to transition Reynolds' approach
from a $\set$-based semantics to a semantics based on
$\omega$-complete partial orders. We denote the category of
$\omega$-complete partial orders ($\oCPO$s) and their sup-preserving
morphisms by $\omega$CPO. The underlying set of an $\oCPO$ $A$ is
denoted $|A|$.  The category $\oCPOR$ of $\oCPO$ relations has
as its objects triples $(A,B,R)$, where $A, B: \oCPO$ and $R:
\rel(|A|, |B|)$ and $(\bigvee_{i < \omega} a_i, \bigvee_{i < \omega}
b_i) \in R$ whenever $(a_i)_{i < \omega}$ and $(b_i)_{i < \omega}$ are
chains in $A$ and $B$, respectively, such that $(a_i,b_i) \in R$ for
all $i$. The category $\oCPOR$ has as its morphisms from $(A,B,R)$ to
$(A',B',R')$ pairs $(f : A \to A',g : B \to B')$ of morphisms in
$\oCPO$ such that $(f\,a, g\,b) \in R'$ whenever $(a,b) \in R$. We
note that if $(f,g) : (A,B,R) \to (A',B',R')$ and $(a_i)_{i < \omega}$
and $(b_i)_{i < \omega}$ are chains in $A$ and $B$, respectively, then
$ (f \, (\bigvee_{i < \omega} a_i), g \, (\bigvee_{i < \omega} b_i)) =
(\bigvee_{i < \omega} (f a_i), \bigvee_{i < \omega} (g b_i)) \in R'$
necessarily holds.  We write $R : \oCPOR(A,B)$ in place of $(A,B,R):
\oCPOR$ when convenient. If $R : \oCPOR(A,B)$ then we write $\pi_1 R$
and $\pi_2 R$ for the {\em domain} $A$ of $R$ and the {\em codomain}
$B$ of $R$, respectively. If $A : \oCPO$, then we write $\Eq_A =
(A,A,\Eq_{|A|})$ for the {\em equality relation} on $A$.

>>>>

To accommodate GADTs, we will need to transition Reynolds' approach
from a $\set$-based semantics to a semantics based on
$\omega$-complete partial orders. We denote the category of
$\omega$-complete partial orders ($\oCPO$s) and their {\color{blue}
  monotone?} sup-preserving morphisms by $\omega$CPO. The underlying
set of an $\oCPO$ $A$ is denoted $|A|$. The category $\oCPOR$ of
$\oCPO$ relations has as its objects triples $(A,B,R)$, where $A, B:
\oCPO$; $R: \rel(|A|, |B|)$; {\color{blue} $(a,b) \in R$, $a \leq a'$,
  and $b \leq b'$ imply $(a',b') \in R$; so next part is redundant?}
and $(\bigvee_{i < \omega} a_i, \bigvee_{i < \omega} b_i) \in R$
whenever $(a_i)_{i < \omega}$ and $(b_i)_{i < \omega}$ are chains in
$A$ and $B$, respectively, such that $(a_i,b_i) \in R$ for all
$i$. The category $\oCPOR$ has as its morphisms from $(A,B,R)$ to
$(A',B',R')$ pairs $(f : A \to A',g : B \to B')$ of morphisms in
$\oCPO$ such that $(f\,a, g\,b) \in R'$ whenever $(a,b) \in R$. We
note that if $(f,g) : (A,B,R) \to (A',B',R')$ and $(a_i)_{i < \omega}$
and $(b_i)_{i < \omega}$ are chains in $A$ and $B$, respectively, then
$ (f \, (\bigvee_{i < \omega} a_i), g \, (\bigvee_{i < \omega} b_i)) =
(\bigvee_{i < \omega} (f a_i), \bigvee_{i < \omega} (g b_i)) \in R'$
necessarily holds.  We write $R : \oCPOR(A,B)$ in place of $(A,B,R):
\oCPOR$ when convenient. If $R : \oCPOR(A,B)$ then we write $\pi_1 R$
and $\pi_2 R$ for the {\em domain} $A$ of $R$ and the {\em codomain}
$B$ of $R$, respectively. If $A : \oCPO$, then we write $\Eq_A =
(A,A,\Eq_{|A|})$ for the {\em equality relation} on $A$.
